Untrusted B2B Collaboration using the Blockchain

### 2018-07-09 paper/paper.tex
Related work

\subsection{Orchestrations and Choreographies}
A work by Weber et. al \citep{weber2016untrusted} showed how to use the blockchain to monitor and coordinate business processes across organizations. They use a smart contract that all parties of a business process communicate with.

@@

%TODO reference original blockchain paper
Blockchain technology is used in cryptocurrencies, most notably Bitcoin \cite{nakamoto2008bitcoin}.
The use in cryptocurrency has laid the foundation for a number of decentralized application besides financial ones.
Ethereum \cite{wood2014ethereum} is a cryptocurrency that also builds on blockchain technologies and allows users to execute code in the form of \emph{smart contracts}.
Smart contracts are Turing complete code artifacts, that can be deployed on the blockchain and have an interface that is callable by users. 
They can receive and send money, store information locally and emit events on the blockchain ledger.
When calling functions on a smart contract, users have to supply \emph{gas}, a unit that powers smart contract computations.
Contracts deplete gas for each operation and return excess gas back to the user.
This ensures that contracts are not running for an unlimited amount of time and that computations on the blockchain are expensive in order to avoid unnecessary operations being performed on-chain.

\subsection{Prior Work on Business Processes on the Blockchain}
%summarize untrusted paper
%summarize Caterpillar
%acknowledge their Work
%display the shortcomings

>>>>

\subsection{Orchestrations and Choreographies}

@@

%TODO reference original blockchain paper
Blockchain technology is used in cryptocurrencies, most notably Bitcoin \cite{nakamoto2008bitcoin}.
The use in cryptocurrency has laid the foundation for a number of decentralized application besides financial ones.
Ethereum \cite{wood2014ethereum} is a cryptocurrency that also builds on blockchain technologies and allows users to execute code in the form of \emph{smart contracts}.
Smart contracts are Turing complete code artifacts, that can be deployed on the blockchain and have an interface that is callable by users. 
They can receive and send money, store information locally and emit events on the blockchain ledger.
When calling functions on a smart contract, users have to supply \emph{gas}, a unit that powers smart contract computations.
Contracts deplete gas for each operation and return excess gas back to the user.
This ensures that contracts are not running for an unlimited amount of time and that computations on the blockchain are expensive in order to avoid unnecessary operations being performed on-chain.
%TODO short text on the paper which shows smart contract examples

\subsection{Prior Work on Business Processes on the Blockchain}
%summarize untrusted paper
%summarize Caterpillar
%acknowledge their Work
%display the shortcomings
A work by Weber et. al \cite{weber2016untrusted} showed how to use the blockchain to monitor and coordinate business processes across organizations.
They use a smart contract that all parties of a business process communicate with.
They also introduce the concept of \emph{triggers}, applications that listen to events on the blockchain and trigger external API calls.
